Submission 1.1

### 2023-08-16 Submission 1.1.tex
Possible contradiction about question 12 (God) - Wanted to figure out how to incorporate the existence of God - Now unresolved - There's a contradiction, but it's the same one as is present in Descartes' cogito

                    $A \iff B$\\
                    $A \land \neg B$\\
                    \rule{5em}{.5pt}\\
                    $C$
          \end{enumerate}
    \item God is omnipotent if and only if He can do everything. If He can't make a stone so heavy that He can't lift it, then he can't do everything. But if He can make a stone so heavy that He can't lift it, He can't do everything. Therefore, either God is not omnipotent or God does not exist. (B 132)
          \begin{enumerate}[(a)]
              \item God is omnipotent if and only if he can do everything.\\
                    If he cannot make a stone so heavy that he cannot lift it, he cannot do everything.\\
                    If he can make a stone that he cannot lift, he cannot do everything.\\
                    \rule{15em}{.5pt}\\
                    Either god is not omnipotent or he does not exist.
              \item The argument is valid. Soudness is difficult to determine.\\
                    \textit{Saffron's Commentary: I have no idea where the existence of God fits into that argument. In the English, it makes sense that it suddenly appears in the conclusion; in the logical notation, less so. I don't know whether that makes it invalid or not.}
              \item \textit{A}: God exists.\\
                    \textit{B}: God is omnipotent.\\
                    \textit{D}: God can do everything.\\
                    \textit{C}: God can make a stone which he cannot lift.\\

                    $B \iff C$\\
                    $\neg D \to \neg C$\\
                    $D \to \neg C$\\
                    \rule{5em}{.5pt}\\
                    $\neg B \lor \neg A$
          \end{enumerate}
\end{enumerate}
\begin{enumerate}
    \setcounter{enumi}{12}
    \item Consider the tic-tac-toe grid with the squares labeled as this:
          \begin{center}
              \begin{tabular}{c|c|c}
                  1 & 2 & 3 \\
                  \hline
                  4 & 5 & 6 \\
                  \hline
                  7 & 8 & 9
              \end{tabular}
          \end{center}
          Suppose that X moves first to square 5, and O moves next to square 4. Prove that X can
          guarantee a win. (Cline)\\\\
          X's next move should be to square 1.
          After these three moves, the board looks like this:
          \begin{center}
            \begin{tabular}{c|c|c}
                X & 2 & 3 \\
                \hline
                O & X & 6 \\
                \hline
                7 & 8 & 9
            \end{tabular}
        \end{center}
         At this point, if O chooses to move to any square other than square 9, X can move to square 9 on the next turn and win. See below for one possible outcome:
         \begin{center}
            \begin{tabular}{c|c|c}
                X & O & 3 \\
                \hline
                O & X & 6 \\
                \hline
                7 & 8 & X
            \end{tabular}
        \end{center}
         If O \textit{does} chose to move to square 9, X can move next to square 3. The board would then look like this:
         \begin{center}
            \begin{tabular}{c|c|c}
                X & 2 & X \\
                \hline
                O & X & 6 \\
                \hline
                7 & 8 & O
            \end{tabular}
        \end{center}
        If O played in any square other than 2, X could play in square 2 on the next turn and win. However, the same is true of square 7: if O plays in any square other than 7, X can then play in square 7 and win. 
        However, O cannot play in both squares 2 and 7 on the same turn. Regardless of where O plays, X will be able to win by playing in either square 2 or square 7.

>>>>

                    $A \iff B$\\
                    $A \land \neg B$\\
                    \rule{5em}{.5pt}\\
                    $C$
          \end{enumerate}
    \item God is omnipotent if and only if He can do everything. If He can't make a stone so heavy that He can't lift it, then he can't do everything. But if He can make a stone so heavy that He can't lift it, He can't do everything. Therefore, either God is not omnipotent or God does not exist. (B 132)
          \begin{enumerate}[(a)]
              \item God is omnipotent if and only if he can do everything.\\
                    If he cannot make a stone so heavy that he cannot lift it, he cannot do everything.\\
                    If he can make a stone that he cannot lift, he cannot do everything.\\
                    \rule{15em}{.5pt}\\
                    Either god is not omnipotent or he does not exist.
              \item The argument is valid. Soudness is difficult to determine.\\
                    \textit{Saffron's Commentary: I have no idea where the existence of God fits into that argument. In the English, it makes sense that it suddenly appears in the conclusion; in the logical notation, less so. I don't know whether that makes it invalid or not.\\
                    Update: It seems like there's a contradiction posed by $\neg D \to \neg C$ and $D \to \neg C$, because the second statemnent is equivalent to $C \to \neg D$, meaning $C \to \neg C$. However, Descartes'} cogito \textit{has the same issue.}
              \item \textit{A}: God exists.\\
                    \textit{B}: God is omnipotent.\\
                    \textit{C}: God can do everything.\\
                    \textit{D}: God can make a stone which he cannot lift.\\

                    $B \leftrightarrow C$\\
                    $\neg D \to \neg C$\\
                    $D \to \neg C$\\
                    \rule{5em}{.5pt}\\
                    $\neg B \lor \neg A$
          \end{enumerate}
\end{enumerate}
\begin{enumerate}
    \setcounter{enumi}{12}
    \item Consider the tic-tac-toe grid with the squares labeled as this:
          \begin{center}
              \begin{tabular}{c|c|c}
                  1 & 2 & 3 \\
                  \hline
                  4 & 5 & 6 \\
                  \hline
                  7 & 8 & 9
              \end{tabular}
          \end{center}
          Suppose that X moves first to square 5, and O moves next to square 4. Prove that X can
          guarantee a win. (Cline)\\\\
          X's next move should be to square 1.
          After these three moves, the board looks like this:
          \begin{center}
            \begin{tabular}{c|c|c}
                X & 2 & 3 \\
                \hline
                O & X & 6 \\
                \hline
                7 & 8 & 9
            \end{tabular}
        \end{center}
         At this point, if O chooses to move to any square other than square 9, X can move to square 9 on the next turn and win. See below for one possible outcome:
         \begin{center}
            \begin{tabular}{c|c|c}
                X & O & 3 \\
                \hline
                O & X & 6 \\
                \hline
                7 & 8 & X
            \end{tabular}
        \end{center}
         If O \textit{does} chose to move to square 9, X can move next to square 3. The board would then look like this:
         \begin{center}
            \begin{tabular}{c|c|c}
                X & 2 & X \\
                \hline
                O & X & 6 \\
                \hline
                7 & 8 & O
            \end{tabular}
        \end{center}
        If O played in any square other than 2, X could play in square 2 on the next turn and win. However, the same is true of square 7: if O plays in any square other than 7, X can then play in square 7 and win. 
        However, O cannot play in both squares 2 and 7 on the same turn. Regardless of where O plays, X will be able to win by playing in either square 2 or square 7.
